---
title: "Team14_Project_Occupancy_Detection"
author: "Prajwal Gonnade, Supreet Nayak"
date: "December 5, 2016"
output: word_document
---

#GLM/LDA/QDA/CART/KNN/Random Forest
#Clear workspace
```{r clr-wksp}
rm(list = ls())
```

```{r load-packages, message=FALSE}
library(boot)
library(caret)
library(class)
library(ROCR)
library(MASS)
library(tree)
library(randomForest)
library(chemometrics)
library(reshape2)
```

#Load CSV
```{r load-csv}
#Select datatraining.txt
Occupancy_Train <- read.csv(file.choose(),header=T)

#Select datatest.txt
Occupancy_Test1 <- read.csv(file.choose(),header=T)

#Select datatest2.txt
Occupancy_Test2 <- read.csv(file.choose(),header=T)
```


#Analyzing Data
```{r analyzing-data}
names(Occupancy_Train)
str(Occupancy_Train)
summary(Occupancy_Train)
boxplot(Occupancy_Train[,-1],las=2)
cor(Occupancy_Train[,-1])
```

#Logistic Regression

glm(Occupancy ~ Temperature + Humidity + Light + CO2 + HumidityRatio, data = Occupancy_Train, family = "binomial")

```{r Initial-Model}
Occupancy_glm <- glm(Occupancy ~ Temperature + Humidity + Light + CO2 + HumidityRatio, data = Occupancy_Train, family = "binomial")
summary(Occupancy_glm)
```

#Explanation -

#Removing insignificant predictors
```{r remove-insig-preds}
summary(glm(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, family = "binomial"))
```


###Final Model -
```{r final-model}
Occupancy_glm <- glm(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, family = "binomial")
```

#Confusion Matrix on Testing Data - 1
```{r confusion-matrix-glm-testdata-1}
glm_probs_1 = predict(Occupancy_glm, Occupancy_Test1, type = "response")
glm_pred_y_1 = rep(0, length(Occupancy_Test1$Occupancy))
glm_pred_y_1[glm_probs_1 > 0.5] = 1
table(glm_pred_y_1, Occupancy_Test1$Occupancy)
mean(glm_pred_y_1 != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, glm_pred_y_1)
Test_MSE <- sum((glm_pred_y_1 - as.numeric(Occupancy_Test1$Occupancy))^2)/nrow(Occupancy_Test1)
Test_MSE
```


#ROC Analysis GLM - 1
```{r roc-analysis-glm-1}
roc.curve=function(s,print=FALSE){
Ps=(glm_probs_1>s)*1
FP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 0))/sum(Occupancy_Test1$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 1))/sum(Occupancy_Test1$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test1$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,], xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve GLM-1', col="green",lwd=2,type="l")
```

#Confusion Matrix on Testing Data - 2
```{r confusion-matrix-glm-testdata-2}
glm_probs_1 = predict(Occupancy_glm, Occupancy_Test2, type = "response")
glm_pred_y_1 = rep(0, length(Occupancy_Test2$Occupancy))
glm_pred_y_1[glm_probs_1 > 0.5] = 1
table(glm_pred_y_1, Occupancy_Test2$Occupancy)
mean(glm_pred_y_1 != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, glm_pred_y_1)
```


#ROC Analysis GLM - 2
```{r roc-analysis-glm-2}
roc.curve=function(s,print=FALSE){
Ps=(glm_probs_1>s)*1
FP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 0))/sum(Occupancy_Test2$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 1))/sum(Occupancy_Test2$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test2$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,], xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve GLM-2', col="green",lwd=2,type="l")
```

#LDA - Testing Data 1
```{r lda-1}
Occupancy_lda <- lda(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
Occupancy_lda
lda_pred = predict(Occupancy_lda, Occupancy_Test1)
names(lda_pred)
table(lda_pred$class, Occupancy_Test1$Occupancy)
mean(lda_pred$class != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy,lda_pred$class)
```

#ROC Analysis LDA - Testing Data 1
```{r roc-analysis-lda-1}
S = lda_pred$posterior[,2]
roc.curve=function(s,print=FALSE){
Ps=(S>s)*1
FP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 0))/sum(Occupancy_Test1$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 1))/sum(Occupancy_Test1$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test1$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve LDA-1', col="green",lwd=2,type="l")
```

#LDA - Testing Data 2
```{r lda-2}
Occupancy_lda <- lda(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
Occupancy_lda
lda_pred = predict(Occupancy_lda, Occupancy_Test2)
names(lda_pred)
table(lda_pred$class, Occupancy_Test2$Occupancy)
mean(lda_pred$class != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy,lda_pred$class)
```

#ROC Analysis LDA - Testing Data 2
```{r roc-analysis-lda-2}
S = lda_pred$posterior[,2]
roc.curve=function(s,print=FALSE){
Ps=(S>s)*1
FP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 0))/sum(Occupancy_Test2$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 1))/sum(Occupancy_Test2$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test2$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve LDA-2', col="green",lwd=2,type="l")
```


#Cross Validation LDA
```{r k-fold-lda}
inds=sample(1:nrow(Occupancy_Train),0.9*nrow(Occupancy_Train))
df.train=Occupancy_Train[inds,]
df.test=Occupancy_Train[-inds,]
train.model = lda(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
preds=predict(train.model, df.test)
```

#ROC Analysis LDA - CV
```{r roc-analysis-lda-cv}
S = preds$posterior[,2]
roc.curve=function(s,print=FALSE){
Ps=(S>s)*1
FP=sum((Ps==1)*(df.test$Occupancy == 0))/sum(df.test$Occupancy == 0)
TP=sum((Ps==1)*(df.test$Occupancy == 1))/sum(df.test$Occupancy == 1)
if(print==TRUE){
print(table(Observed=df.test$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve LDA-CV', col="green",lwd=2,type="l")
```


#QDA - Testing Data 1
```{r qda-1}
Occupancy_qda <- qda(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
Occupancy_qda
qda.pred <- predict(Occupancy_qda, Occupancy_Test1)
table(qda.pred$class, Occupancy_Test1$Occupancy)
mean(qda.pred$class != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy,qda.pred$class)
```

#ROC Analysis QDA - Testing Data 1
```{r roc-analysis-qda-1}
S = qda.pred$posterior[,2]
roc.curve=function(s,print=FALSE){
Ps=(S > s)*1
FP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 0))/sum(Occupancy_Test1$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 1))/sum(Occupancy_Test1$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test1$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve QDA-1', col="green",lwd=2,type="l")
```

#QDA - Testing Data 2
```{r qda-2}
Occupancy_qda <- qda(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
Occupancy_qda
qda.pred <- predict(Occupancy_qda, Occupancy_Test2)
table(qda.pred$class, Occupancy_Test2$Occupancy)
mean(qda.pred$class != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy,qda.pred$class)
```

#ROC Analysis QDA - Testing Data 2
```{r roc-analysis-qda-2}
S = qda.pred$posterior[,2]
roc.curve=function(s,print=FALSE){
Ps=(S > s)*1
FP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 0))/sum(Occupancy_Test2$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 1))/sum(Occupancy_Test2$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test2$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve QDA-2', col="green",lwd=2,type="l")
```

#Cross Validation QDA - 10 Fold
```{r k-fold-qda}
inds=sample(1:nrow(Occupancy_Train),0.9*nrow(Occupancy_Train))
df.train=Occupancy_Train[inds,]
df.test=Occupancy_Train[-inds,]
train.model = qda(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
preds=predict(train.model, df.test)
```

#ROC Analysis QDA - CV
```{r roc-analysis-qda-cv}
S = preds$posterior[,2]
roc.curve=function(s,print=FALSE){
Ps=(S>s)*1
FP=sum((Ps==1)*(df.test$Occupancy == 0))/sum(df.test$Occupancy == 0)
TP=sum((Ps==1)*(df.test$Occupancy == 1))/sum(df.test$Occupancy == 1)
if(print==TRUE){
print(table(Observed=df.test$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)',main = 'ROC Curve QDA-CV', col="green",lwd=2,type="l")
```


#CART - Testing Data 1
```{r cart-1}
set.seed(2)
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
str(Occupancy_Train)
tree.Occupancy_Train <- tree(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
plot(tree.Occupancy_Train)
summary(tree.Occupancy_Train)
text(tree.Occupancy_Train, pretty = 0)
tree.pred <- predict(tree.Occupancy_Train, Occupancy_Test1, type = "class")
table(tree.pred, Occupancy_Test1$Occupancy)
mean(tree.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, tree.pred)
```

#Cross Validation and Pruning - Testing Data 1
```{r prune-1}
set.seed(3)
cv.Occupancy_Train <- cv.tree(tree.Occupancy_Train, FUN=prune.misclass)
names(cv.Occupancy_Train)
cv.Occupancy_Train
par(mfrow = c(1,2))
plot(cv.Occupancy_Train$size, cv.Occupancy_Train$dev, type = "b")
plot(cv.Occupancy_Train$k, cv.Occupancy_Train$dev, type = "b")
prune.Occupancy_Train = prune.misclass(tree.Occupancy_Train, best = 9)
#prune.mt2Data_Train = prune.misclass(tree.mt2Data_Train)
plot(prune.Occupancy_Train)
text(prune.Occupancy_Train, pretty = 0)
tree.pred = predict(prune.Occupancy_Train, Occupancy_Test1, type = "class")
#tree.pred = predict(prune.mt2Data_Train, mt2Data_Test)
table(tree.pred, Occupancy_Test1$Occupancy)
mean(tree.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, tree.pred)
```

#ROC Analysis Decision Trees - Testing Data 1
```{r roc-analysis-trees-1}
tree.pred = predict(prune.Occupancy_Train, Occupancy_Test1, type = "vector")
#tree.prob <- attr(tree.pred, "vector") 
roc.curve=function(s,print=FALSE){
Ps=(tree.pred[,2]>s)*1
FP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 0))/sum(Occupancy_Test1$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 1))/sum(Occupancy_Test1$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test1$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)', main = 'ROC Curve Decision Tree-1', col="green",lwd=2,type="l")
```


#CART - Testing Data 2
```{r cart-2}
set.seed(2)
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
str(Occupancy_Train)
tree.Occupancy_Train <- tree(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train)
plot(tree.Occupancy_Train)
summary(tree.Occupancy_Train)
text(tree.Occupancy_Train, pretty = 0)
tree.pred <- predict(tree.Occupancy_Train, Occupancy_Test2, type = "class")
table(tree.pred, Occupancy_Test2$Occupancy)
mean(tree.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, tree.pred)
```

#Cross Validation and Pruning - Testing Data 2
```{r prune-2}
set.seed(3)
cv.Occupancy_Train <- cv.tree(tree.Occupancy_Train, FUN=prune.misclass)
names(cv.Occupancy_Train)
cv.Occupancy_Train
par(mfrow = c(1,2))
plot(cv.Occupancy_Train$size, cv.Occupancy_Train$dev, type = "b")
plot(cv.Occupancy_Train$k, cv.Occupancy_Train$dev, type = "b")
prune.Occupancy_Train = prune.misclass(tree.Occupancy_Train, best = 9)
#prune.mt2Data_Train = prune.misclass(tree.mt2Data_Train)
plot(prune.Occupancy_Train)
text(prune.Occupancy_Train, pretty = 0)
tree.pred = predict(prune.Occupancy_Train, Occupancy_Test2, type = "class")
#tree.pred = predict(prune.mt2Data_Train, mt2Data_Test)
table(tree.pred, Occupancy_Test2$Occupancy)
mean(tree.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, tree.pred)
```

#ROC Analysis Decision Trees - Testing Data 2
```{r roc-analysis-trees-2}
tree.pred = predict(prune.Occupancy_Train, Occupancy_Test2, type = "vector")
#tree.prob <- attr(tree.pred, "vector") 
roc.curve=function(s,print=FALSE){
Ps=(tree.pred[,2]>s)*1
FP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 0))/sum(Occupancy_Test2$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 1))/sum(Occupancy_Test2$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test2$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)', main = 'ROC Curve Decision Tree-2', col="green",lwd=2,type="l")
```

###KNN Testing Data 1 
#KNN k = 1
```{r knn-k-1-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 1, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```

#KNN k = 3
```{r knn-k-3-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 3, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```


#KNN k = 5
```{r knn-k-5-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 5, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```

#KNN k = 10
```{r knn-k-10-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 10, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```

#KNN k = 25
```{r knn-k-25-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 25, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```

#KNN k = 50
```{r knn-k-50-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 50, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```

#KNN k = 100
```{r knn-k-100-1}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test1$Occupancy <- factor(Occupancy_Test1$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test1))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 100, prob = TRUE)
table(knn.pred, Occupancy_Test1$Occupancy)
mean(knn.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, knn.pred)
```

###KNN Testing Data 2
#KNN k = 1
```{r knn-k-1-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 1, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```

#KNN k = 3
```{r knn-k-3-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 3, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```


#KNN k = 5
```{r knn-k-5-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 5, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```

#KNN k = 10
```{r knn-k-10-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 10, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```

#KNN k = 25
```{r knn-k-25-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 25, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```

#KNN k = 50
```{r knn-k-50-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 50, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```

#KNN k = 100
```{r knn-k-100-2}
Occupancy_Train$Occupancy <- factor(Occupancy_Train$Occupancy)
Occupancy_Test2$Occupancy <- factor(Occupancy_Test2$Occupancy)
attach(Occupancy_Train)
test.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Test2))]
train.X = cbind(Temperature, Light, CO2, HumidityRatio)[as.numeric(rownames(Occupancy_Train))]
Occupancy_Train.Occupancy = Occupancy[1:nrow(Occupancy_Train)]
set.seed(1)
knn.pred = knn(data.frame(train.X), data.frame(test.X), Occupancy_Train.Occupancy, k = 100, prob = TRUE)
table(knn.pred, Occupancy_Test2$Occupancy)
mean(knn.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, knn.pred)
```

#Random Forest Bag - Testing Data 1
```{r random-forest-bag-1}
set.seed(123)
bag.Occupancy_Train = randomForest(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, mtry = 4, importance = TRUE)
bag.Occupancy_Train
yhat.bag = predict(bag.Occupancy_Train, Occupancy_Test1)
plot(yhat.bag, Occupancy_Test1$Occupancy)
abline(0,1)
mean((as.numeric(yhat.bag) - as.numeric(Occupancy_Test1$Occupancy)) ^ 2)
```

#Random Forest Ntree
```{r random-forest-ntree-1}
set.seed(123)
bag.Occupancy_Train = randomForest(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, mtry = 4, ntree = 15)
bag.Occupancy_Train
yhat.bag = predict(bag.Occupancy_Train, Occupancy_Test1)
plot(yhat.bag, Occupancy_Test1$Occupancy)
abline(0,1)
mean((as.numeric(yhat.bag) - as.numeric(Occupancy_Test1$Occupancy)) ^ 2)
```

#Random Forest
```{r random-forest-1}
set.seed(123)
rf.Occupancy_Train = randomForest(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, mtry = 4, importance = TRUE)
rf.Occupancy_Train
yhat.rf = predict(bag.Occupancy_Train, Occupancy_Test1)
plot(yhat.rf, Occupancy_Test1$Occupancy)
abline(0,1)
mean((as.numeric(yhat.rf) - as.numeric(Occupancy_Test1$Occupancy)) ^ 2)
importance(rf.Occupancy_Train)
varImpPlot(rf.Occupancy_Train)
```

#Random Forst Confusion Matrix
```{r rf-confusion-matrix-1}
rf.pred <- predict(rf.Occupancy_Train, Occupancy_Test1, type = "class")
table(rf.pred, Occupancy_Test1$Occupancy)
mean(rf.pred != Occupancy_Test1$Occupancy)
confusionMatrix(Occupancy_Test1$Occupancy, rf.pred)
```

#ROC Analysis Random Forest
```{r roc-analysis-rf-1}
rf.pred = predict(rf.Occupancy_Train, Occupancy_Test1, type = "prob")
#tree.prob <- attr(tree.pred, "vector") 
roc.curve=function(s,print=FALSE){
Ps=(rf.pred[,2]>s)*1
FP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 0))/sum(Occupancy_Test1$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test1$Occupancy == 1))/sum(Occupancy_Test1$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test1$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)', main = 'ROC Curve Random Forest-1', col="green",lwd=2,type="l")
```

#Random Forest Bag - Testing Data 2
```{r random-forest-bag-2}
set.seed(123)
bag.Occupancy_Train = randomForest(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, mtry = 4, importance = TRUE)
bag.Occupancy_Train
yhat.bag = predict(bag.Occupancy_Train, Occupancy_Test2)
plot(yhat.bag, Occupancy_Test2$Occupancy)
abline(0,1)
mean((as.numeric(yhat.bag) - as.numeric(Occupancy_Test2$Occupancy)) ^ 2)
```

#Random Forest Ntree
```{r random-forest-ntree-2}
set.seed(123)
bag.Occupancy_Train = randomForest(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, mtry = 4, ntree = 15)
bag.Occupancy_Train
yhat.bag = predict(bag.Occupancy_Train, Occupancy_Test2)
plot(yhat.bag, Occupancy_Test2$Occupancy)
abline(0,1)
mean((as.numeric(yhat.bag) - as.numeric(Occupancy_Test2$Occupancy)) ^ 2)
```

#Random Forest
```{r random-forest-2}
set.seed(123)
rf.Occupancy_Train = randomForest(Occupancy ~ Temperature + Light + CO2 + HumidityRatio, data = Occupancy_Train, mtry = 4, importance = TRUE)
rf.Occupancy_Train
yhat.rf = predict(bag.Occupancy_Train, Occupancy_Test2)
plot(yhat.rf, Occupancy_Test2$Occupancy)
abline(0,1)
mean((as.numeric(yhat.rf) - as.numeric(Occupancy_Test2$Occupancy)) ^ 2)
importance(rf.Occupancy_Train)
varImpPlot(rf.Occupancy_Train)
```

#Random Forst Confusion Matrix
```{r rf-confusion-matrix-2}
rf.pred <- predict(rf.Occupancy_Train, Occupancy_Test2, type = "class")
table(rf.pred, Occupancy_Test2$Occupancy)
mean(rf.pred != Occupancy_Test2$Occupancy)
confusionMatrix(Occupancy_Test2$Occupancy, rf.pred)
```

#ROC Analysis Random Forest
```{r roc-analysis-rf-2}
rf.pred = predict(rf.Occupancy_Train, Occupancy_Test2, type = "prob")
#tree.prob <- attr(tree.pred, "vector") 
roc.curve=function(s,print=FALSE){
Ps=(rf.pred[,2]>s)*1
FP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 0))/sum(Occupancy_Test2$Occupancy == 0)
TP=sum((Ps==1)*(Occupancy_Test2$Occupancy == 1))/sum(Occupancy_Test2$Occupancy == 1)
if(print==TRUE){
print(table(Observed=Occupancy_Test2$Occupancy,Predicted=Ps))
}
vect=c(FP,TP)
names(vect)=c("FPR","TPR")
return(vect)
}
threshold = 0.5
roc.curve(threshold,print=TRUE)
ROC.curve=Vectorize(roc.curve)
M.ROC=ROC.curve(seq(0,1,by=.01))
plot(M.ROC[1,],M.ROC[2,],xlab='False positive rate(1-specificity)', ylab='True positive rate(specificity)', main = 'ROC Curve Random Forest-2', col="green",lwd=2,type="l")
```